Tutorial_4

### 2024-12-16 Tutorial_4.Rmd
updated the way osf data is read in by checking if it exists first

```{r load-pkg, results='hide'}
pkg <- c("cmdstanr", "standist", "tidyverse", "RColorBrewer", "patchwork", 
         "brms", "tidybayes", "bayesplot", "future", "parallel", "VGAM", "faux",
         "rstan", "osfr")

@@

```{r load-osf-sim1, eval=F}
## create a relevant folder
dir.create("Tutorial_4_planning/data/sim1/")

## read in the data from the OSF and store it in a relevant folder
osf_sim1_data <-
  # retrieve the OSF (main) project
  osf_retrieve_node("3dbcs") %>% 
  # list files in this repository - there must be a more efficient way than this...
  osf_ls_files(pattern = "Tutorial_4_planning") %>%
  osf_ls_files(pattern = "data") %>%
  osf_ls_files(pattern = "sim1") %>%
  osf_ls_files(pattern = "sim1_data") %>%
  osf_download(path = "./Tutorial_4_planning/data/sim1/")
```

@@

```{r load-osf-sim2, eval=F}
## create a relevant folder
dir.create("Tutorial_4_planning/data/sim2/")

## read in the data from the OSF and store it in a relevant folder
osf_sim2_data <-
  # retrieve the OSF (main) project
  osf_retrieve_node("3dbcs") %>% 
  # list files in this repository - there must be a more efficient way than this...
  osf_ls_files(pattern = "Tutorial_4_planning") %>%
  osf_ls_files(pattern = "data") %>%
  osf_ls_files(pattern = "sim2") %>%
  osf_ls_files(pattern = "sim2_data") %>%
  osf_download(path = "./Tutorial_4_planning/data/sim2/")
```

>>>>

```{r load-pkg, results='hide'}
pkg <- c("cmdstanr", "standist", "tidyverse", "RColorBrewer", "patchwork", 
         "brms", "tidybayes", "bayesplot", "future", "parallel", "VGAM", "faux",
         "rstan", "osfr", "here")

@@

If necessary, read it from the OSF to start with (because it is a large file). 
This step is only required to be done once.
After that, the file will be in your local directory and you can skip this chunk in the future.

```{r load-osf-sim1, eval=T}
## create a relevant folder, if it does not already exist
sim1_output_dir <- here("Tutorial_4_planning/data/sim1/")

if (!dir.exists(here(sim1_output_dir))) {
  dir.create(here(sim1_output_dir))
}

## read in the data from the OSF and store it in a relevant folder, if it does not already exist
sim1_file_name <- here("Tutorial_4_planning/data/sim1/sim1_data.csv")

if (!file.exists(here(sim1_file_name))) {
  osf_retrieve_node("3dbcs") %>% 
  osf_ls_files(pattern = "Tutorial_4_planning") %>%
  osf_ls_files(pattern = "data") %>%
  osf_ls_files(pattern = "sim1") %>%
  osf_ls_files(pattern = "sim1_data") %>%
  osf_download(path = sim1_output_dir)
}
```

@@

```{r load-osf-sim2, eval=T}
## create a relevant folder, if it does not already exist
sim2_output_dir <- here("Tutorial_4_planning/data/sim2/")

if (!dir.exists(here(sim2_output_dir))) {
  dir.create(here(sim2_output_dir))
}

## read in the data from the OSF and store it in a relevant folder, if it does not already exist
sim2_file_name <- here("Tutorial_4_planning/data/sim2/sim2_data.csv")

if (!file.exists(here(sim2_file_name))) {
  osf_retrieve_node("3dbcs") %>% 
  osf_ls_files(pattern = "Tutorial_4_planning") %>%
  osf_ls_files(pattern = "data") %>%
  osf_ls_files(pattern = "sim2") %>%
  osf_ls_files(pattern = "sim2_data") %>%
  osf_download(path = sim2_output_dir)
}
```
